---
title: "`r params$docTitle`"
date: "`r format(Sys.Date())`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    fig_caption: false
params:
    docTitle: "BRICK Heating System Report"
    file: "BRICK_Heating_System_report.csv"
    path: "C:/Users/ricardar/Documents/Results/BRICK/calibration-tests/fromRobin/calibration-2015-CP_2026-04-21_12.17.30/"
    scenNames: NULL
    name: ""
    region: "DEU"
---

```{r setup, include=FALSE}
library(dplyr) #nolint: undesirable_function_linter.
library(ggplot2) #nolint: undesirable_function_linter.

knitr::opts_chunk$set(
  echo = FALSE,
  error = TRUE,
  message = FALSE,
  warning = FALSE
)
```

```{r set variables, check existence of first file}

# Assemble the file path
filePath <- file.path(params$path, params$file)

if (length(filePath) > 1) {
  stop("plotsLcc.Rmd only runs on a single file.")
}

# Check if the file exists
if (!file.exists(filePath)) {
  message("No BRICK_Heating_System_report.csv file found. ",
          "BRICK_Heating_System_report.csv is produced by running reportHeatingSystemDetails(<path>).")
  knitr::knit_exit()
}

config <- yaml::read_yaml(file.path(params$path, "config", "config_COMPILED.yaml"))
tmpl <- config[["reportingTemplate"]]

outName <- params$name
outPath <- dirname(filePath[1])


```

```{r Read in data}
dataTmp <- utils::read.csv(filePath)
data <- dataTmp %>%
  filter(typ == "Res" | is.na(typ)) # Temporary

if (!identical(params$region, "all")) data <- filter(data, .data$region %in% c(params$region, NA))
```

# Lifetime distribution estimates

## Lifetime distributions of standing stock

### Lifetime estimate

```{r Plot lt of standing stock}

showAnalysisPlot("line", data, "Lifetime|Initial Stock", yname = "relVal", color = "hs", rprt = "vin",
                 xlabName = "Time of removal", ylabName = "Share of standing stock in 2000",
                 tmpl = tmpl, linetype = "hs")

```

### Lifetime estimate compared to maximum lifetime

```{r Plot initial stock leave time estimate and max lifetime}
showAnalysisPlot("line", data, c("Lifetime|Initial Stock", "Max Lifetime|Initial Stock"),
                 yname = "relVal", color = "hs",
                 remCols = c("value", "absVal"), rprt = "vin",
                 xlabName = "Time of removal", ylabName = "Share of standing stock in 2000",
                 tmpl = tmpl, linetype = "variable")
```

### Lifetime estimate, remaining share

```{r Plot leave time estimate of initial stock, remaining share}

showAnalysisPlot("line", data, c("Remaining Share|Initial Stock", "Max Remaining Share|Initial Stock"),
                 yname = "relVal", color = "hs", rprt = "vin",
                 suppressLateTtot = FALSE,
                 xlabName = "Time", ylabName = "Share of remaining floorspace", tmpl = tmpl,
                 linetype = "variable")

```

## Lifetime estimates of new constructions

### Lifetime estimate

```{r Plot lt of constructions}

showAnalysisPlot("line", data, "Lifetime|Construction", yname = "relVal", color = "hs", rprt = "ttotIn",
                 xlabName = "Time of removal", ylabName = "Share of initial construction", tmpl = tmpl, linetype = "hs")

```

### Lifetime estimate compared to maximum lifetime

```{r Plot mixed construction leave time estimate and max lifetime}
showAnalysisPlot("line", data, c("Lifetime|Construction", "Max Lifetime|Construction"), yname = "relVal", color = "hs",
                 remCols = c("value", "absVal"), rprt = "ttotIn",
                 xlabName = "Time of removal", ylabName = "Quantity in million m2", tmpl = tmpl, linetype = "variable")
```

### Lifetime estimate, remaining share

```{r Plot leave time of construction, remaining share}

showAnalysisPlot("line", data, c("Remaining Share|Construction", "Max Remaining Share|Construction"), yname = "relVal",
                 color = "hs", rprt = "ttotIn",
                 xlabName = "Time", ylabName = "Share of remaining floorspace", tmpl = tmpl,
                 linetype = "variable")

```

## Lifetime distribution of renovations

### Lifetime estimate

```{r Plot lt of renovations}

showAnalysisPlot("line", data, "Lifetime|Renovation|Agg: vin", yname = "relVal", color = "hs", rprt = "ttotIn",
                 xlabName = "Time of removal", ylabName = "Share of initial renovation", tmpl = tmpl, linetype = "hs")

showAnalysisPlot("line", data, "Lifetime|Renovation", yname = "relVal",
                 color = "hs", rprt = c("vin", "ttotIn"),
                 xlabName = "Time of removal", ylabName = "Share of initial renovation", tmpl = tmpl, linetype = "hs")

```

### Lifetime estimate compared to maximum lifetime

```{r Plot mixed renovation leave time estimate and max lifetime}

showAnalysisPlot("line", data, c("Lifetime|Renovation|Agg: vin", "Max Lifetime|Renovation|Agg: vin"),
                 yname = "relVal", color = "hs",
                 remCols = c("value", "absVal"), rprt = "ttotIn",
                 xlabName = "Time of removal", ylabName = "Quantity in million m2", tmpl = tmpl, linetype = "variable")

showAnalysisPlot("line", data, c("Lifetime|Renovation", "Max Lifetime|Renovation"), yname = "relVal", color = "hs",
                 remCols = c("value", "absVal"), rprt = c("vin", "ttotIn"),
                 xlabName = "Time of removal", ylabName = "Quantity in million m2", tmpl = tmpl, linetype = "variable")
```


### Lifetime estimate, remaining share

```{r Plot leave time of renovations, remaining share}

showAnalysisPlot("line", data, c("Remaining Share|Renovation", "Max Remaining Share|Renovation"), yname = "relVal",
                 color = "hs", rprt = c("vin", "ttotIn"),
                 xlabName = "Time", ylabName = "Share of remaining floorspace", tmpl = tmpl,
                 linetype = "variable")

```

## Verification of lifetime inequality

```{r Plot left-hand side and right-hand side of lifetime inequality}

showAnalysisPlot("twoBar", data, c("Lifetime Inequality|lhs", "Lifetime Inequality|rhs"), yname = "value",
                 color = "hs", rprt = "vin",
                 xlabName = "Time of removal", ylabName = "Quantity in million m2", tmpl = tmpl)
```


# Lifecycle costs (LCC)

## LCC of construction

```{r Plot LCC of construction}
showAnalysisPlot("bar", data, "LCC|Construction",
                 xname = "hs", yname = "value", color = "costType", rprt = c("ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Heating System", ylabName = "Costs in USD/m2", tmpl = tmpl)
```

## LCC of renovation

### Averaged across vintages

```{r Plot LCC of renovation, agg vin}
showAnalysisPlot("bar", data, c("LCC|Renovation|Agg: vin", "Brick Share|Renovation|Agg: vin"),
                 xname = "hsr", yname = "value", color = "costType", rprt = c("ttotIn", "typ", "loc"),
                 facets = "hs", xlabName = "Final Heating System", ylabName = "Costs in USD/m2", tmpl = tmpl,
                 valueCap = 1500, capCol = "Investment (intangible)",
                 addPoints = list(variable = "Brick Share|Renovation|Agg: vin",
                                  yname = "value", y2labName = "Brick Share"))
```

```{r Plot LCC of renovation, agg vin, no facets}
showAnalysisPlot("bar", data %>% filter(hs == "gabo"), c("LCC|Renovation|Agg: vin", "Brick Share|Renovation|Agg: vin"),
                 xname = "hsr", yname = "value", color = "costType", rprt = c("ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Final Heating System", ylabName = "Costs in USD/m2", tmpl = tmpl,
                 valueCap = 1500, capCol = "Investment (intangible)",
                 addPoints = list(variable = "Brick Share|Renovation|Agg: vin",
                                  yname = "value", y2labName = "Brick Share"))
```

### At full resolution

```{r Plot LCC of renovation}
showAnalysisPlot("bar", data, c("LCC|Renovation", "Brick Share|Renovation"),
                 xname = "hsr", yname = "value", color = "costType", rprt = c("vin", "ttotIn", "typ", "loc"),
                 facets = "hs", xlabName = "Final Heating System", ylabName = "Costs in USD/m2", tmpl = tmpl,
                 valueCap = 1500, capCol = "Investment (intangible)",
                 addPoints = list(variable = "Brick Share|Renovation", yname = "value", y2labName = "Brick Share"))
```

```{r Plot LCC of renovation, only hs gabo}
showAnalysisPlot("bar", data %>% filter(.data$hs == "gabo"), c("LCC|Renovation", "Brick Share|Renovation"),
                 xname = "hsr", yname = "value", color = "costType", rprt = c("vin", "ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Final Heating System", ylabName = "Costs in USD/m2", tmpl = tmpl,
                 valueCap = 1500, capCol = "Investment (intangible)",
                 addPoints = list(variable = "Brick Share|Renovation", yname = "value", y2labName = "Brick Share"))
```

## LCC of renovation, matrix charts

### Pie chart

#### Averaged across vintages

```{r Plot renovation LCC as pie matrix, agg vin}
showAnalysisPlot("pieChart", data, "LCC|Renovation|Agg: vin",
                 xname = "hs", yname = "hsr", valueName = "value", color = "costType",
                 rprt = c("ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Original Heating System", ylabName = "Final Heating System", tmpl = tmpl,
                 valueCap = 1500)
```

#### At full resolution

```{r Plot renovation LCC as pie matrix}
showAnalysisPlot("pieChart", data, "LCC|Renovation",
                 xname = "hs", yname = "hsr", valueName = "value", color = "costType",
                 rprt = c("vin", "ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Original Heating System", ylabName = "Final Heating System", tmpl = tmpl,
                 valueCap = 1500)
```

### Heat Map

#### Averaged across vintages

```{r Plot renovation LCC as heat map matrix, agg vin}
showAnalysisPlot("heatMap", data, "LCC|Renovation|Agg: vin",
                 xname = "hs", yname = "hsr", valueName = "value", rprt = c("ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Original Heating System", ylabName = "Final Heating System", tmpl = tmpl,
                 valueCap = 1500)
```

#### At full resolution

```{r Plot renovation LCC as heat map matrix}
showAnalysisPlot("heatMap", data, "LCC|Renovation",
                 xname = "hs", yname = "hsr", valueName = "value", rprt = c("vin", "ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Original Heating System", ylabName = "Final Heating System", tmpl = tmpl,
                 valueCap = 1500)
```

# Levelized costs of heat (LCOH)

## LCOH of construction

```{r Plot LCOH of construction}
showAnalysisPlot("bar", data, "LCOH|Construction",
                 xname = "hs", yname = "value", color = "costType", rprt = c("ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Final Heating System", ylabName = "Costs in US Cents/kWh", tmpl = tmpl)
```

## LCOH of renovation

### Averaged across vintages

```{r Plot LCOH of renovation, agg vin}
showAnalysisPlot("bar", data, c("LCOH|Renovation|Agg: vin", "Brick Share|Renovation|Agg: vin"),
                 xname = "hsr", yname = "value", color = "costType", rprt = c("ttotIn", "typ", "loc"),
                 facets = "hs", xlabName = "Final Heating System", ylabName = "Costs in US Cents/kWh", tmpl = tmpl,
                 valueCap = 100, capCol = "Investment (intangible)",
                 addPoints = list(variable = "Brick Share|Renovation|Agg: vin",
                                  yname = "value", y2labName = "Brick Share"))
```

```{r Plot LCOH of renovation, agg vin, no facets}
showAnalysisPlot("bar", data %>% filter(.data$hs == "gabo"),
                 c("LCOH|Renovation|Agg: vin", "Brick Share|Renovation|Agg: vin"),
                 xname = "hsr", yname = "value", color = "costType", rprt = c("ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Final Heating System", ylabName = "Costs in US Cents/kWh", tmpl = tmpl,
                 valueCap = 100, capCol = "Investment (intangible)",
                 addPoints = list(variable = "Brick Share|Renovation|Agg: vin",
                                  yname = "value", y2labName = "Brick Share"))
```

### At full resolution

```{r Plot LCOH of renovation}
# Can decrease valueCap to valueCap = 50 and set fixedYlim = valueCap for comparable plots
showAnalysisPlot("bar", data, c("LCOH|Renovation", "Brick Share|Renovation"),
                 xname = "hsr", yname = "value", color = "costType", rprt = c("vin", "ttotIn", "typ", "loc"),
                 facets = "hs", xlabName = "Final Heating System", ylabName = "Costs in US Cents/kWh", tmpl = tmpl,
                 valueCap = 100, capCol = "Investment (intangible)",
                 addPoints = list(variable = "Brick Share|Renovation", yname = "value", y2labName = "Brick Share"))
```

```{r Plot LCOH of renovation, filter gabo}
showAnalysisPlot("bar", data %>% filter(.data$hs == "gabo"), c("LCOH|Renovation", "Brick Share|Renovation"),
                 xname = "hsr", yname = "value", color = "costType", rprt = c("vin", "ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Final Heating System", ylabName = "Costs in US Cents/kWh", tmpl = tmpl,
                 valueCap = 100, capCol = "Investment (intangible)",
                 addPoints = list(variable = "Brick Share|Renovation", yname = "value", y2labName = "Brick Share"))
```

## LCOH of renovation with mixed lifetimes, matrix charts

### Pie chart

#### Averaged across vintages

```{r Plot renovation LCOH as pie matrix, agg vin}
showAnalysisPlot("pieChart", data, "LCOH|Renovation|Agg: vin",
                 xname = "hs", yname = "hsr", color = "costType", valueName = "value",
                 rprt = c("ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Original Heating System", ylabName = "Final Heating System", tmpl = tmpl,
                 valueCap = 100)
```

#### At full resolution

```{r Plot renovation LCOH as pie matrix}
showAnalysisPlot("pieChart", data, "LCOH|Renovation",
                 xname = "hs", yname = "hsr", color = "costType", valueName = "value",
                 rprt = c("vin", "ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Original Heating System", ylabName = "Final Heating System", tmpl = tmpl,
                 valueCap = 100)
```

### Heat map

#### Averaged across vintages

```{r Plot renovation LCOH as heat map, agg vin}
showAnalysisPlot("heatMap", data, "LCOH|Renovation|Agg: vin",
                 xname = "hs", yname = "hsr", valueName = "value",
                 rprt = c("ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Original Heating System", ylabName = "Final Heating System", tmpl = tmpl,
                 valueCap = 100)
```

#### At full resolution

```{r Plot renovation LCOH as heat map}
showAnalysisPlot("heatMap", data, "LCOH|Renovation",
                 xname = "hs", yname = "hsr", valueName = "value",
                 rprt = c("vin", "ttotIn", "typ", "loc"),
                 facets = NULL, xlabName = "Original Heating System", ylabName = "Final Heating System", tmpl = tmpl,
                 valueCap = 100)
```

## LCOH time evolution

```{r Plot renovationLCOH by time and hsr}
showAnalysisPlot("line", data, "LCOH|Renovation|Agg: hs, vin",
                 xname = "ttotIn", yname = "value", color = "hsr", rprt = c("typ", "loc"),
                 sumUp = "costType",
                 facets = NULL, xlabName = "Time of installation", ylabName = "Costs in US Cents/kWh",
                 tmpl = tmpl, linetype = "hsr")
```

```{r Plot renovation LCOH by time, hsr and cost type, agg hs vin}
showAnalysisPlot("bar", data, "LCOH|Renovation|Agg: hs, vin",
                 xname = "ttotIn", yname = "value", color = "costType", rprt = c("typ", "loc"),
                 facets = "hsr", xlabName = "Time of installation", ylabName = "Costs in US Cents/kWh",
                 tmpl = tmpl, valueCap = 150)
```

```{r Plot renovation LCOH by time, hsr and cost type}
dataLcohTime <- data %>%
  filter(.data$variable == "LCOH|Renovation") %>%
  group_by(across(all_of(c("costType", "hs", "hsr", "vin", "typ", "loc")))) %>%
  filter(length(.data$ttotIn) >= 3) %>%
  ungroup()

showAnalysisPlot("bar", dataLcohTime, "LCOH|Renovation",
                 xname = "ttotIn", yname = "value", color = "costType", rprt = c("hs", "vin", "typ", "loc"),
                 facets = "hsr", xlabName = "Time of installation", ylabName = "Costs in US Cents/kWh",
                 tmpl = tmpl, valueCap = 150)
```

# Logit shares compared to Brick shares

## Shares of renovation

### Aggregated across all hs

```{r Plot Logit and brick Share, agg hs}
showAnalysisPlot("twoBar", data, c("Brick Share|Renovation|Agg: hs", "Logit Share|Renovation|Agg: hs"),
                 yname = "value", xname = "ttotIn", color = "hsr", rprt = "vin",
                 xlabName = "Time of installation", ylabName = "Shares", tmpl = tmpl,
                 filterRows = NULL)
```

### Energy ladder 1

```{r Plot Logit and brick Share, energy ladder 1, agg hs}
showAnalysisPlot("twoBar", data,
                 c("Brick Share|Renovation|Energy Ladder 1|Agg: hs", "Logit Share|Renovation|Energy Ladder 1|Agg: hs"),
                 yname = "value", xname = "ttotIn", color = "hsr", rprt = "vin",
                 xlabName = "Time of installation", ylabName = "Shares", tmpl = tmpl,
                 filterRows = NULL)
```

### Aggregated across all vintages

```{r Plot Logit and brick Share, agg vin}
showAnalysisPlot("twoBar", data, c("Brick Share|Renovation|Agg: vin", "Logit Share|Renovation|Agg: vin"),
                 yname = "value", xname = "hs", color = "hsr", rprt = "ttotIn",
                 xlabName = "Time of installation", ylabName = "Shares", tmpl = tmpl,
                 filterRows = NULL)
```

### Full resolution

```{r Plot Logit and brick Share, by hs}
showAnalysisPlot("twoBar", data, c("Brick Share|Renovation", "Logit Share|Renovation"),
                 yname = "value", xname = "hs", color = "hsr", rprt = c("vin", "ttotIn"),
                 xlabName = "Previous heating system", ylabName = "Shares", tmpl = tmpl,
                 filterRows = NULL)
```

# Heating system ratio by LCC differences

```{r Plot hs ratio by lcc difference}
slopeRenHS <- - data$value[data$variable == "Price Sensitivity|Heating System|Renovation"]
renInRatioVar <- unique(grep("^Log Ratio to (.*)\\|Renovation", data$variable, value = TRUE))
renLccDiffVar <- unique(grep("^LCC Difference to (.*)\\|Renovation", data$variable, value = TRUE))
hsRef <- sub("^Log Ratio to (.*)\\|Renovation", "\\1", renInRatioVar)
showAnalysisPlot("scatter", data, c(renInRatioVar, renLccDiffVar),
                 yname = renInRatioVar, xname = renLccDiffVar, valueName = "value",
                 xlabName = paste("Difference of LCC with", hsRef),
                 ylabName = paste("Log ratio of renovated floorspace w.r.t to", hsRef),
                 color = "hsr", rprt = c("vin"), tmpl = tmpl, shape = "ttotIn", slope = slopeRenHS, fitLinear = TRUE)
```
